Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-14 proposal/mprop.tex
Finish proposed approach section

The study has 
\textbf{Independent Variables}: components of tickets - stack traces, steps
to reproduce, grammar error free description and summary, succinct/detailed 
summary, complex/light discussion in comments

\textbf{Dependent Variable}: duration of the ticket between OPEN status and
CLOSED status.

Research questions, outline experimental design, independent variables, dependent variables.

state how you propose to solve the software development problem. Show that your proposed approach is feasible, but identify any risks.

>>>>

The independent variables we would like to test are:
  \begin{itemize}
    \item presence and number of stack traces in a ticket;
    \item steps to reproduce (as described above - images or text);
    \item presence of screenshots in tickets;
    \item text components (e.g. summary, description) being either 
      succinct or detailed;
    \item grammar-free textual description;
    \item overall sentiment drawn from comments (e.g. angry or calm);
    \item complex or light discussion in comments.
  \end{itemize}

In terms of dependant variables, we only have one - the time it takes
between when the ticket was created and marked as OPEN until when it
is finished and marked as CLOSED or RESOLVED.
